\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-29 related_work.tex
Updated the paper

Other works such as Quartz~\cite{glog02} and Bertin
et.al.~\cite{Bertin:2000:TVR:1947412.1947439}, also incorporate delay
statements in Esterel using \texttt{pause} and special \textit{pragmas}
(annotations), respectively.  The Quartz solution is targeted at
studying timing properties using model checkers rather than
implementation, like us. The solution introduced by Bertin
et.al.~\cite{Bertin:2000:TVR:1947412.1947439} translates real-time
pragmas into Timed automata~\cite{alur94} for model-checking real-time
deadlines. Our solution on the other hand removes all continuous time
elements and produces single discrete time model thereby making the
solution amenable to existing functional and real-time verification
tools developed for reactive languages and more in the spirit of logical
time. Finally, a major difference between Bertin et.al and our approach
is that their approach requires programmers to annotate the time taken
by 'C' code fragments manually, this is extremely error prone, we use
static low-level program analysis to find out such times automatically.

>>>>

Other works such as Quartz~\cite{glog02} and Bertin et
al.~\cite{Bertin:2000:TVR:1947412.1947439}, also incorporate delay
statements in Esterel using \texttt{pause} and special \textit{pragmas}
(annotations), respectively.  The Quartz solution is targeted at
studying timing properties using model checkers rather than
implementation, like us. The solution introduced by Bertin et
al.~\cite{Bertin:2000:TVR:1947412.1947439} translates real-time pragmas
into Timed automata~\cite{alur94} for model-checking real-time
deadlines. Our solution on the other hand removes all continuous time
elements and produces single discrete time model thereby making the
solution amenable to existing functional and real-time verification
tools developed for reactive languages and more in the spirit of logical
time. Finally, a major difference between Bertin et al and our approach
is that their approach requires programmers to annotate the time taken
by 'C' code fragments manually, this is extremely error prone, we use
static low-level program analysis to find out such times automatically.
